How Well do we Teach Cybersecurity?\\(Abstract 20 January, Paper 27th)

### 2019-01-02 ITiCSE2019.tex
Added Michael Page quote on skil shortage
Minor comments from paper chat

Specialist curricula abound: a recent one is \cite{ACMIEEEAISSIGSECIFIP}. However, given the shortage of specialists, in practice a good generalist with some CyberSecurity expertise can often get a ``specialist'' job.
\subsection{Research Questions}
\begin{enumerate}
\item The person in teh street --- probably not.
\item The general CS graduate.
\item The general CS masters graduate.
\item The specialist CS graduate.
\item The specialist CS masters graduate.
\end{enumerate}
\section{Policy Context}

@@

\subsection{Staff}
JHD possibly to write about his recruitment experiences.  ? more IoC input?

>>>>

Specialist curricula abound: a recent one is \cite{ACMIEEEAISSIGSECIFIP}. However, given the shortage of specialists, in practice a good generalist with some CyberSecurity expertise can often get a ``specialist'' job.
\subsection{Research Questions}
\begin{enumerate}
\item The person in the street --- probably not. ({\emph{interesting point from a public engagement/science communication perspective -- aren't ``we'' trying to create a digitally competent and capable citizenry? Minor point but maybe worth mentioning e.g. being safe online, accessing public services, etc}})
\item The general CS graduate.
\item The general CS masters graduate.
\item The specialist CS graduate.
\item The specialist CS masters graduate.
\end{enumerate}
\section{Policy Context}

@@

\subsection{Staff}
It is well known that CyberSecurity skills are in short supply, for example \cite{Page2018a}.
\begin{quote}

\end{quote}
JHD possibly to write about his recruitment experiences.  ? more IoC input?
